\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

    \moveleft.5\hoffset\centerline{\large\bf Esref Ozturk} % Your name at the top

    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

    \moveleft.5\hoffset\centerline{esrefozturk.com} % Your address

    \moveleft.5\hoffset\centerline{esref@esrefozturk.com} % Your address

    \moveleft.5\hoffset\centerline{+90 506 861 26 78} % Your address

    \begin{resume}


        \section{EMPLOYMENT}

        {\bf Senior Software Engineer} \hfill (February 2018 - Present) \\
        {\bf Toptal}, Remote \\
        Toptal is an exclusive network of the top freelance software developers.
        \begin{itemize}
            \item Worked with clients from all over the world. {\bf  SF, NY, London, Spain}
            \item Developed scalable web applications. {\bf Django, Node.js, React, Vue.js }
            \item Developed robust mobile applications. {\bf Android, iOS, Swift, Objective-C }
            \item Worked with AWS technologies. {\bf EC2, S3, Lambda, Beanstalk, Serverless }
        \end{itemize}

        {\bf Co-Founder} \hfill (April 2017 - January 2020) \\
        {\bf Drive Buddy Inc.}, METU Technopolis \\
        Drive Buddy is an AI-powered mobile telematics solution.
        \begin{itemize}
            \item Managed the team of 2-5.
            \item Created a machine-learning algorithm to detect car accidents. {\bf LSTM, Keras }
        \end{itemize}

        {\bf Software Engineer} \hfill (June 216 - June 2017) \\
        {\bf Udemy Inc.}, METU Technopolis \\
        Udemy is an online learning platform.
        \begin{itemize}
            \item R\&D on search functionality of the website. {\bf Django, Elasticsearch, Angular }
            \item Migrated Elasticsearch from 1.5 to 2x. {\bf Ansible  }
        \end{itemize}

        {\bf Software Engineer} \hfill (February 2016 - May 2016) \\
        {\bf STM Defence Technologies \& Engineering Inc.},  Ankara \\
        STM is a company focused on Defence Technologies.
        \begin{itemize}
            \item Developed a system to automated hardening.  {\bf Hardening, Python }
        \end{itemize}

        {\bf Software Developer} \hfill (April 2014 - January 2016) \\
        {\bf Cyber Warfare Lab, Labris Networks }, METU Technopolis \\
        Labris Networks specializes in Unified Threat Management.
        \begin{itemize}
            \item R\&D on Labris Unified Threat Management machine. {\bf C++, Bash, UTM  }
        \end{itemize}

        {\bf Contracted Software Developer} \hfill (June 2014 - September 2014) \\
        {\bf TUBITAK(The Scientific and Technological Research Council of Turkey) } \\
        TUBITAK is national science, technology and innovation agency of Turkey.
        \begin{itemize}
            \item Developed a Debian kernel module for multiple clipboards. {\bf Kernel Hooks }
        \end{itemize}

        {\bf Software Engineering Intern} \hfill (June 2014 - July 2014) \\
        {\bf Hazelcast }, Istanbul R\&D Office \\
        Hazelcast is the industry leading in-memory computing platform.
        \begin{itemize}
            \item Developed sample Hazelcast integration modules. {\bf Java, Hazelcast, Spring }
        \end{itemize}

        {\bf Software Engineering Intern} \hfill (June 2013 - September 2013) \\
        {\bf Kovan Research Lab }, METU \\
        KOVAN research lab is founded to study the synthesis of intelligent systems.
        \begin{itemize}
            \item Developed a web application for instructors to prepare exams. {\bf Django, Mysql }
        \end{itemize}



        \section{PUBLICATIONS}
        \begin{itemize}
        		\item  Demirpolat, A., Ergenc, D., {\bf Ozturk, E.}, Onur, E. 2018. ”Software-defined Network Security”. Enabling Technologies and Architecture for Next-Generation Networking Capabilities. IGI Global.

        \end{itemize}
        


        \section{EDUCATION}

        {\bf M.S., Computer Engineering } \hfill {(Dropout)}\\
        Middle East Technical University,Ankara, Turkey

        {\bf B.S., Computer Engineering } \hfill {(Graduation: June 2016)}\\
        Middle East Technical University,Ankara, Turkey


        \section{TECHNICAL EXPERIENCE}

        {\bf ADSES} \hfill (September 2016 - December 2019) \\
        \textit{https://github.com/esrefozturk/adses}
        \begin{itemize}
            \item ADSES utilizes blockchain to store voting data transparently, albeit securely.
        \end{itemize}

        {\bf POA} \hfill (March 2018 - April 2018) \\
        \textit{https://github.com/esrefozturk/poa}
        \begin{itemize}
            \item Proof of Authority Blockchain from scratch
        \end{itemize}

        {\bf Pwner} \hfill (January 2014 - Present) \\
        \textit{www.0xdeffbeef.com}
        \begin{itemize}
            \item Practicing information security topics, organizing and participating Capture the Flag Competitions.
        \end{itemize}

        {\bf Checkmate} \hfill (September 2014 - January 2015) \\
        \textit{CheckmateChess.github.io}
        \begin{itemize}
            \item Web application for playing chess running GNUChess in the background.
        \end{itemize}

       

        {\bf Hypnos} \hfill (September 2015 - Present) \\
        \textit{senior.ceng.metu.edu.tr/2016/newline}
        \begin{itemize}
            \item Personalized sleep tracking and analyzing system that focuses on optimizing people's sleep. {\bf Arduino, Raspberry Pi, Android, Python, Django, Machine Learning }
        \end{itemize}


        \section{AWARDS \& HONORS}
        \begin{itemize}
            \itemsep -2pt % Reduce space between items
            \item {\bf First Place}, CTF, Prodaft/Invictus Europe, Turkey, May 2016
            \item {\bf First Place}, CTF, STM Defence Technologies \& Engineering Inc., Turkey, Oct 2015
            \item {\bf First Place}, Web Application CTF, Ankara University \& Octosec Information Security Team, Turkey, May 2014
            \item {\bf First Place of Turkey}, 67th Team of All, IEEEXtreme Programming Competition 9.0, Oct 2015
            \item {\bf Second Place}, among foreign participants, Open All-Ukrainian Collegiate Programming Contest, Ukraine, Oct 2014
            \item {\bf Honorable Mention}, Hash Code, Google, Feb 2016
            \item {\bf Honorable Mention}, ACM ICPC, SEERC, Ukraine, Oct 2014
            \item {\bf Honorable Mention}, ACM ICPC, SEERC, Ukraine, Oct 2013
            \item {\bf Honorable Mention}, IEEEXtreme Programming Competition 7.0, Oct 2013
            \item {\bf Honorable Mention}, IEEEXtreme Programming Competition 6.0, Oct 2012
            \item {\bf Honorable Mention}, IEEEXtreme Programming Competition 5.0, Oct 2011
            \item {\bf High Honor Student}, METU Computer Engineering, Feb 2016
            \item {\bf Certificate}, Google Developer Challenge Scholarship, Udacity, Nov 2017
            \item {\bf Certificate}, MCNA - Network(Fast), Middle East Technical University - Continuous Education Center, May 2014
        \end{itemize}



       % \section{EXTRA-CURRICULAR \\ ACTIVITIES}

        %\begin{itemize}
        %    \itemsep -2pt % Reduce space between items
         %   \item Active member of METU-CENG ACM Student Chapter
         %   \item SAYOKAN (Turkish Martial Art)
          %  \item Student Member of IEEE (2011-Present)
         %   \item Student Member of ACM (2013-Present)
        %\end{itemize}


        %\section{ABOUT} Programming for 6 years. Mostly interested in contributing open
        %source, system hacking, operating systems and participating in programming contests.








        %\section{LANGUAGE}

        %\begin{itemize} \itemsep -2pt % Reduce space between items
        %\item Turkish (Native)
        %\item English (Fluent)
        %\end{itemize}




        %\section{TECHNICAL \\ SKILLS}

        %\begin {tabular}{llll}
        %\\

        %C/C++ (6 years) & Python (4 years) & Bash (3 years) & SQL (2 years) \\
        %Javascript (2 years) & Php (1 year) & Django (2 year) & Java (1 year) \\
        %.NET (3 years)
        %\end{tabular}














    \end{resume}
\end{document}
